---
title: 'nausea: Nowcasting Under Structural Breaks'
output:
  pdf_document: default
  html_document:
    df_print: paged
  rmarkdown::html_vignette: default
vignette: |
  %\VignetteIndexEntry{nausea} %\VignetteEngine{knitr::rmarkdown} \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
library("mosumfvar")
library("nowcasting")
```

## Getting data

`get_data` will download current vintage data from the NYFED and FREDMD databases up to a given date, defaulting to June 2021. These are subjected to stationarity transforms.

```{r}
data_vignette <- get_data()
```

By default, we include a version up to May 2021.
```{r}
data(panel)
```



## Data segmentation with `mosumfvar`

Based on the `mosumvar` package and methodology, `mosumfvar` will perform change point analysis on the panel assuming a static factor model with low-dimensional vector autoregression (VAR) dynamics on the factors. 
The number of factors `q`,
the VAR order `order`, 
and the bandwidth `G` can all be selected from the data. 
 
```{r}
mosumfvar_out <- mosumfvar(panel$panel, q = 2, order = 1, method = "Score") 
```



## Forecasting

`ar.weighted` can be used to fit a VAR to the factor series, where the data is weighted adaptively to the estimated change points.
The choices are for the weights are `linear`,`exp`, or `robust`. 

```{r}
# forecast factors
factors <- mosumfvar_out$fm$factors
ar.mod <- ar.weighted(factors, cps = mosumfvar_out$seg$cps)
factor_fcast <- predict(ar.mod, factors, n.ahead = 5)
ts.plot(factor_fcast$pred, main = "factor forecast")
# forecast panel
panel_fcast <- factor_fcast$pred %*% t(mosumfvar_out$fm$loadings)
ts.plot(panel_fcast, main = "panel forecast")
```



## Nowcasting

Nowcasting of the GDP component can be performed with e.g. a linear regression model via `lm`, which permits use of the `predict` method. 

```{r}
lm_data <- data.frame(gdp = panel$gdp, factors)
gdp_lm <- lm(gdp ~ ., data = lm_data)
gdp_lm
plot.ts(gdp_lm$fitted.values, xlab = "Time (Quarter)", ylab = "smoothed change in gdp")
predict(gdp_lm, newdata = data.frame(gdp = NA, panel_fcast))
```


